Copy number inference with InferCNV

### 2024-05-15 analyses/cell-type-ewings/04-infercnv.Rmd
update png paths

@@

![InferCNV Heatmap - Endothelial cells as reference](`r file.path(all_results_dir_list["with_ref"], "infercnv.png")`)

@@

![InferCNV Heatmap - No reference](`r file.path(all_results_dir_list["no_ref"], "infercnv.png")`)

>>>>

# png ref files 
png_files <- file.path(all_results_dir_list, glue::glue("{params$library_id}_infercnv.png")) |> 
  purrr::set_names(names(all_results_dir_list))

@@

![InferCNV Heatmap - Endothelial cells as reference](`r png_files["with_ref"]`)

@@

![InferCNV Heatmap - No reference](`r png_files["no_ref"]`)
